|

### 2021-07-27 prova_knit_finale.Rmd
aggiunta a header

header-includes:
- \def\code#1{\texttt{#1}}
- \usepackage{babel} 
- \usepackage{amssymb}
- \usepackage{amsfonts}
- \usepackage{txfonts}
- \usepackage{amsmath}
- \usepackage{mathtools}
- \usepackage[bindingoffset=1.5cm, left=3cm, right=3cm, top=3cm, bottom=3cm]{geometry}
- \usepackage{graphicx}
- \usepackage{MnSymbol} %allows to insert the QED at the end of the proofs
- \usepackage{hyperref} %set the hyperlink to cite sections, equations...
- \urlstyle{same}
- \usepackage[toc,page]{appendix}
- \usepackage{comment}
- \usepackage{enumitem}
- \usepackage{ntheorem}
- \usepackage{lipsum}
- \usepackage{xcolor}
- \theoremstyle{break}
- \newtheorem{thm}{Theorem}% theorem counter resets every \subsection
- \renewcommand{\thethm}{\arabic{thm}}
- \newtheorem{proposition}{Proposition}
- \newtheorem{assumption}{Assumption}
- \newtheorem{lemma}{Lemma}
- \newtheorem{definition}{Definition}
- \theoremstyle{nonumberplain}
- \newtheorem{proof*}{Proof.}
- \renewcommand{\P}{\mathbb{P}}
- \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
- \def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
- \setcounter{MaxMatrixCols}{10}
- \setlength{\oddsidemargin}{.0in}
- \setlength{\textwidth}{6 in}
- \setlength{\topmargin}{-.1in}
- \setlength{\textheight}{8.1in}
- \renewcommand{\baselinestretch}{1.5}
- \newcommand{\E}{\mathbb E}
- \newcommand{\Q}{\mathbb Q}
- \newcommand{\M}{\mathbb M}
- \newcommand{\R}{\mathbb R}
- \newcommand{\B}{\mathcal B}
- \newcommand{\X}{\mathcal X}
- \newcommand{\Y}{\mathcal Y}
- \newcommand{\Pd}{\mathbb P}
- \newcommand{\N}{\mathcal N}
- \newtheorem{algorithm}{Algorithm}[section]
- \usepackage{float}
- \floatplacement{figure}{}

@@

\subsection{Sequential Importance Sampling}

>>>>

header-includes:
- \def\code#1{\texttt{#1}}
- \usepackage{babel} 
- \usepackage{amssymb}
- \usepackage{amsfonts}
- \usepackage{txfonts}
- \usepackage{amsmath}
- \usepackage{mathtools}
- \usepackage[bindingoffset=1.5cm, left=3cm, right=3cm, top=3cm, bottom=3cm]{geometry}
- \usepackage{graphicx}
- \usepackage{MnSymbol} %allows to insert the QED at the end of the proofs
- \usepackage{hyperref} %set the hyperlink to cite sections, equations...
- \urlstyle{same}
- \usepackage[toc,page]{appendix}
- \usepackage{comment}
- \usepackage{enumitem}
- \usepackage{ntheorem}
- \usepackage{lipsum}
- \usepackage{xcolor}
- \usepackage{mathtools}
- \theoremstyle{break}
- \newtheorem{thm}{Theorem}% theorem counter resets every \subsection
- \renewcommand{\thethm}{\arabic{thm}}
- \newtheorem{proposition}{Proposition}
- \newtheorem{assumption}{Assumption}
- \newtheorem{lemma}{Lemma}
- \newtheorem{definition}{Definition}
- \theoremstyle{nonumberplain}
- \newtheorem{proof*}{Proof.}
- \renewcommand{\P}{\mathbb{P}}
- \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
- \def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
- \setcounter{MaxMatrixCols}{10}
- \setlength{\oddsidemargin}{.0in}
- \setlength{\textwidth}{6 in}
- \setlength{\topmargin}{-.1in}
- \setlength{\textheight}{8.1in}
- \renewcommand{\baselinestretch}{1.5}
- \newcommand{\E}{\mathbb E}
- \newcommand{\Q}{\mathbb Q}
- \newcommand{\M}{\mathbb M}
- \newcommand{\R}{\mathbb R}
- \newcommand{\B}{\mathcal B}
- \newcommand{\X}{\mathcal X}
- \newcommand{\Y}{\mathcal Y}
- \newcommand{\Pd}{\mathbb P}
- \newcommand{\N}{\mathcal N}
- \newtheorem{algorithm}{Algorithm}[section]
- \usepackage{float}
- \floatplacement{figure}{}

@@

\subsection{Sequential Importance Sampling}\label{seq_impt_sampling}
